TITLE

### 2021-02-26 outputs/Paper.Rmd
update

# Data 
In this report, we use the R statistical programming language [@citeR]. To be specific, we use the “tidyverse” package to process data [@citetidyverse], "kableExtra" package to generate tables [@citekableExtra],  ADD ANY PACKAGE HERE. The survey conducted by Petit Poll collects the following data:

@@

```{r salary distribution, echo=FALSE}
sd1<-
  ggplot(simulated_data, aes(x = simulated_data$Q9, fill=type)) +
  geom_histogram(position = "dodge", bins = 30,binwidth = 0.5) +
  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
  labs(title="The salary distributions was higher for teatment group", x="Salary", y="Number of employee")+
  geom_density()
sd1
```

@@

```{r pie1, fig.cap = "Restaurant franchise distribution", echo=FALSE, fig.width=7, fig.height=15}

@@

#Merge twp graphs
ggarrange(
  Pie1, Pie2, 
  ncol = 2, nrow = 1,
  hjust = -0.5,
  align = "hv"
  )
```
* The polar chart illustrates the employee numbers distribution, as can be seen in figure below. (Figure \@ref(fig:employee)) Because of COVID rule, no restaurant is allowed to open for large group dine in. So in the control group, there is 0 restaurant which has more than 30 employees. Most of restaurant has 10 to 20 employees.

>>>>

# Data 
In this report, we use the R statistical programming language [@citeR]. To be specific, we use the “tidyverse” package to process data [@citetidyverse], "kableExtra" package to generate tables [@citekableExtra],  "ggplot2" is used to draw diagrams [@gg1] ADD ANY PACKAGE HERE. The survey conducted by Petit Poll collects the following data:

@@

```{r salary distribution, echo=FALSE}
sd1<-
  ggplot(simulated_data, aes(x = simulated_data$Q9, fill=type)) +
  geom_histogram(position = "dodge", bins = 30,binwidth = 0.5) +
  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
  labs(title="The salary distributions was higher for teatment group", x="Salary", y="Number of employee")+
  geom_density()
```

@@

```{r pie1, fig.cap = "Restaurant franchise distribution", echo=FALSE, fig.width=10, fig.height=5}

@@

#Merge twp graphs
ggarrange(
  Pie1, Pie2, 
  ncol = 2, nrow = 1,
  hjust = -0.5,
  align = "hv"
  )
```

* The polar chart illustrates the employee numbers distribution, as can be seen in figure below. (Figure \@ref(fig:employee)) Because of COVID rule, no restaurant is allowed to open for large group dine in. So in the control group, there is 0 restaurant which has more than 30 employees. Most of restaurant has 10 to 20 employees.
